Estimating Neighborhood Rents with Scraped Data

### 2018-07-27 manuscript/manuscript.Rmd
In the manuscript file now.

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess and Sarah Chasins"
output:
  html_document:
    df_print: paged
abstract: Online classified ads are a key source of information about local rental
  housing markets. This research first assesses the agreement of census tract rent
  estimates based on scraped rental advertisements with existing data sources. The
  second component of the paper investivates temporal and spatial dynamics in one-bedroom
  rents among Seattle neighborhoods using spatial models. Posterior distributions
  of all model hyperparameters and parameters are estimated with integrated nested
  Laplace approximations (INLA). Training data for models cover quarterly tract estimates
  for Q2 2017 through Q1 2018, while the test data are Q2 2018 median values as observed.
  The top model assumes that spatial and temporal dynamics are separable, i.e. independent
  of each other, and non-interactive. This spatial random-effects model with AR(1)
  temporal structure achieves a mean absolute error (MAE) of about $100 for the training
  data and $140 for the test data.
---

@@

Figure 5 shows a scatter plot/bubble plot of 2000-definition Census tract one-bedroom rent estimates between Craigslist and Dupre+Scott for the 80 tracts where comparable estimates exist (i.e. about 2/3 of the 124 2000-definition tracts in Seattle). The purple dashed line indicates the loess smoother fit between the measures. Looking at the measure comparison, the first takeaway is that there is strong correlation ($r = .82$) and relative agreement between the measures (mean absolute difference = $186). The Craigslist measure reflects asking rents and the Dupre+Scott measure reflects contract rents for a neighborhood (i.e. the asking rent less an incentives a landlord offers). Given the currently low vacancy rates in most properties, the only neighborhoods where there would theoretically be more salience to the asking vs contract rent distinction (i.e. a wider gap in these indicators) are at the high end of the distribution where demand for luxury apartments has slackened some. At the high-end of the neighborhood rent distribution, however, Craigslist and Dupre+Scott are in arguably the strongest agreement.

@@

![Scatter plot of neighborhood 1-bedroom rents across Craigslist and Dupre+Scott. Craigslist represents median asking rent among all one-bedroom listings, Dupre+Scott consists of median contract rents among one-bedroom units in 20+ unit properties. Purple dashed line indicates loess fit.](../output/rent_scatter_across_1B.png)

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess and Sarah Chasins"
output:
  html_document:
    df_print: paged
abstract: Online classified ads are a key source of information about local rental
  housing markets. This research first assesses the agreement of census tract rent
  estimates based on scraped rental advertisements with existing data sources. The
  second component of the paper investigates temporal and spatial dynamics in one-bedroom
  rents among Seattle neighborhoods using spatial models. Posterior distributions
  of all model hyperparameters and parameters are estimated with integrated nested
  Laplace approximations (INLA). Training data for models cover quarterly tract estimates
  for Q2 2017 through Q1 2018, while the test data are Q2 2018 median values as observed.
  The top model assumes that spatial and temporal dynamics are separable, i.e. independent
  of each other, and non-interactive. This spatial random-effects model with AR(1)
  temporal structure achieves a mean absolute error (MAE) of about $100 for the training
  data and $140 for the test data.
---

@@

Figure 5 shows a scatter plot/bubble plot of 2000-definition Census tract one-bedroom rent estimates between Craigslist and Dupre+Scott for the 80 tracts where comparable estimates exist (i.e. about 2/3 of the 124 2000-definition tracts in Seattle). The purple dashed line indicates the LOESS smoother fit between the measures. Looking at the measure comparison, the first takeaway is that there is strong correlation ($r = .82$) and relative agreement between the measures (mean absolute difference = $186). The Craigslist measure reflects asking rents and the Dupre+Scott measure reflects contract rents for a neighborhood (i.e. the asking rent less an incentives a landlord offers). Given the currently low vacancy rates in most properties, the only neighborhoods where there would theoretically be more salience to the asking vs contract rent distinction (i.e. a wider gap in these indicators) are at the high end of the distribution where demand for luxury apartments has slackened some. At the high-end of the neighborhood rent distribution, however, Craigslist and Dupre+Scott are in arguably the strongest agreement.

@@

![Scatter plot of neighborhood 1-bedroom rents across Craigslist and Dupre+Scott. Craigslist represents median asking rent among all one-bedroom listings, Dupre+Scott consists of median contract rents among one-bedroom units in 20+ unit properties. Purple dashed line indicates LOESS fit.](../output/rent_scatter_across_1B.png)
